Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-03-22 paper/self_calibration_I.tex
euclid: fixed abstract sentence
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@20474 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\begin{abstract}
We study the self-calibration -- the determination of a complex system
response from science data alone -- for precise photometric catalogs
from wide-field imaging surveys. We create an artificial sky of sources
and synthetically observe it under four basic survey strategies,
creating an end-to-end simulation of an imaging survey for each. These
catalog-level simulations include realistic measurement uncertainties
and a complex, position-dependent instrument response. We then use a
self-calibration technique to recover the instrument response by
simultaneously fitting for all the star fluxes and the parameters of a
position-dependent flat-field, optimizing a justified likelihood
function.  For realism, we deliberately fit with a wrong noise model
and a flat-field functional basis that does not include the model that
generated the synthetic data.  We demonstrate that with a favorable
survey strategy, a complex (but smooth) instrument response can be
precisely self-calibrated. We also find that returning the same
sources to very different focal plane positions is the key property of
any survey strategy designed for accurate retrospective
calibration. The results of this work suggest the following advice for
those considering the design of large-scale imaging surveys: Do not
use a regular tiling of the sky; instead return the same sources to
very different focal plane positions.
\end{abstract}

>>>>

\begin{abstract}
We study the self-calibration -- the determination of a complex system
response from science data alone -- for precise photometric catalogs
from wide-field imaging surveys. We create an artificial sky of sources
and synthetically observe it under four basic survey strategies,
creating an end-to-end simulation of an imaging survey for each. These
catalog-level simulations include realistic measurement uncertainties
and a complex, position-dependent instrument response. In the
self-calibration step, we simultaneously fit for all the star fluxes
and the parameters of a position-dependent flat-field.  For realism,
we deliberately fit with a wrong noise model and a flat-field
functional basis that does not include the model that generated the
synthetic data.  We demonstrate that with a favorable survey strategy,
a complex (but smooth) instrument response can be precisely
self-calibrated. We also find that returning the same sources to very
different focal plane positions is the key property of any survey
strategy designed for accurate retrospective calibration. The results
of this work suggest the following advice for those considering the
design of large-scale imaging surveys: Do not use a regular tiling of
the sky; instead return the same sources to very different focal plane
positions.
\end{abstract}
